Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Update comment
Add missing commas

    \begin{itemize}
        \item test discovery is not an aspect of BDD, only an emphasis
            on automating things is an aspect of BDD, so that
            \emph{testing is more fun} and \emph{things e.g. work with
            CI}.  This are two things, but both justify automation.
            We only need this to justify our discussion of Cabal
            integration and automatic test discovery.  If we remove
            those, we do not state that ``automation is an important
            aspect of BDD''.  This may be a solution.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but that we do not cover them.  This
            is very important.  And I think meaning got lost with the
            change, hence the revert.
    \end{itemize}
\end{quote}

@@

Hspec is thus useful for \emph{code documentation} but we observed that parts
of a specification can be useful as user documentation. To that end, 
Python's {\tt doctest} module~\cite{doctest} is of interest for us.
It is not commonly described as a BDD tool, but we think it can be
used for BDD.
There is a Haskell version called Doctest\footnote{%
http://hackage.haskell.org/package/doctest}, which is integrated with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} from Haddock comments and
verifies them automatically.

We will show how to use Doctest and Hspec in combination to design,
document and test Haskell code.
Both, Doctest and Hspec are missing some features.  So we extend them
as needed.  In particular, our contributions are:

>>>>

    \begin{itemize}
        \item test discovery is not an aspect of BDD, only an emphasis
            on automating things is an aspect of BDD, so that
            \emph{testing is more fun} and \emph{things e.g. work with
            CI}.  This are two things, but both justify automation.
            We only need this to justify our discussion of Cabal
            integration and automatic test discovery.  If we remove
            those, we do not state that ``automation is an important
            aspect of BDD''.  This may be a solution.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but that we do not cover them.  This
            is very important.  And I think that meaning got lost with
            the change, hence the revert.
    \end{itemize}
\end{quote}

@@

Hspec is thus useful for \emph{code documentation}, but we observed that parts
of a specification can be useful as user documentation. To that end, 
Python's {\tt doctest} module~\cite{doctest} is of interest for us.
It is not commonly described as a BDD tool, but we think it can be
used for BDD.
There is a Haskell version called Doctest\footnote{%
http://hackage.haskell.org/package/doctest}, which is integrated with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} from Haddock comments and
verifies them automatically.

We will show how to use Doctest and Hspec in combination, to design,
document and test Haskell code.
Both, Doctest and Hspec are missing some features.  So we extend them
as needed.  In particular, our contributions are:
